Hierarchical Inference of the Intrinsic Ellipticity Distribution of Galaxies during Weak Lensing Analysis

### 2013-04-03 docs/ms.tex
Update ms.tex

The distortion in Weak lensing is typically ~ 0.01,or ~0.001 for
galaxy-galaxy lensing it's usually more than 10 times smaller than
the intrinsic shape noise,it's also smaller than the distortion caused
be PSF effect which usually has ~0.05 level. For shear measurement
the main source of uncertainty comes from the intrinsic shape noise
. We know little knowledge about the distribution of intrinsic ellipticity,exception
the assumption that the orientational angle should be isotropic. With
this assumption,we can use the average of galaxies' ellipticity as
an estimator of tangential shear.--However by doing this we lose some
information about how the ellipticity are distributed. Simple average
point estimator can't use the other reasonable assumption about intrinsic
shape distribution --galaxies in different sky patches should have
the same shape distibution--which is the result of homogeneous Universe.

The typical procedure of weak lensing analysis usually include ellipticity
measurement,shear inference,mass profile reconstruction. The measurement
of galaxy shapes is the first step of weak gravitational lensing analysis,since
it's the direct observable that relates with tangential shear.However
in this paper we only concern about how to infere shear from galaxy
ellipticity in a hierachical way.Therefore in our simulation we set
up a simple toy model in which we have the observed ellipticity as
data,and the only measurement error we consider is a Gaussian noise
added on the lensed galaxy ellipticity.We also suppose there is a uniform shear
acting on one all the galaxies in sky patch,

>>>>

The distortion in Weak lensing is typically ~ 0.01,or ~0.001 for
galaxy-galaxy lensing. It's usually more than 10 times smaller than
the intrinsic shape noise,it's also smaller than the distortion caused
be PSF effect which is usually around ~0.05 level. For shear measurement
the main source of uncertainty comes from the intrinsic shape noise
.Since the unlensed galaxy shape can not be observed directly the information
we have about the intrinsic ellipticity is scarce,other than  the assumption that 
the orientational angle should be isotropic. With
this assumption,an estimator can be made by simply averaging galaxies' complex
ellipticity.However by doing this we will not be able to utilize the
information about how the ellipticity are distributed. Simple average
point estimator can't use the other reasonable assumption about intrinsic
shape distribution --galaxies in different sky patches should have
the same shape distibution--which is the natural result of the homogeneous Universe.

A typical procedure of weak lensing analysis  includes ellipticity
measurement,shear inference and mass profile reconstruction. The measurement
of galaxy shapes is the first step of weak gravitational lensing analysis,since
it's the direct observable that relates with tangential shear.However
in this paper we only concern about how to infere shear from galaxy
ellipticity in a hierachical way.Therefore in our simulation we set
up a simple toy model in which we have the observed ellipticity as
data,and the only measurement error we consider is a Gaussian noise
added on the lensed galaxy ellipticity.We also suppose there is a uniform shear
acting on one all the galaxies in sky patch,
